---
title: "CA w2 workshop"
author: "Sennan Cai"
date: "2024-06-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
```

Question 1

```{r}
firemen.data <- read.csv(file='firemen.csv', header=TRUE)

round(cor(firemen.data %>% select_if(is.numeric)),2)


```
a)
..

b)
0.99 and 0.85 between dispatch and damage, attended


Question 2

```{r}
fit = lm(damage ~ attended, data = firemen.data)
summary(fit)
```
a)

positive coefficient and p value is less than 2*10^-16, which is statistically significant

b)

it make theoretically sense because worth the incident we have we need more firemen 
and worth the incident will potentially cause more damage.

Question c

```{r}
fit = lm(damage ~ attended + grade, data = firemen.data)
summary(fit)
```

a)
15.555
b)
0.8126
c)
```{r}
fit = lm(damage ~ attended + factor(grade), data = firemen.data)
summary(fit)
```

0.864

F
```{r}
fit=lm(damage~attended + dispatch  + factor(grade), data = firemen.data)
summary(fit)
```

d)

```{r}
fit = lm(damage ~ dispatch + factor(grade),data=firemen.data)
summary(fit)
```

coefficient is positive 

e)

```{r}
fit=lm(dispatch~attended+factor(grade), data=firemen.data)
summary(fit)
```

Question G

```{r}
data2 = read.csv('fire_building.csv', header = TRUE)
firemen.data <- cbind(firemen.data,data2[2])
```

```{r}
fit=lm(damage~attended + dispatch + trucks + factor(grade) + building.size, data=firemen.data)
summary(fit)
AIC(fit)
```

question h

```{r}
z.multiple=summary(lm(damage~scale(attended)+scale(dispatch)+scale(trucks)+scale(grade)+scale(building.size),data=firemen.data))$coefficients[2:6,]
barplot(z.multiple[,1],beside=T, legend=c("z-scores"))
```

question I

```{r}
fit=lm(log(damage)~attended + dispatch  + factor(grade), data = firemen.data)
summary(fit)
```

```{r}
fit=lm(damage~attended + dispatch  + factor(grade), data = firemen.data)
summary(fit)
```



